\documentclass[reqno,10pt,a4paper,oneside,draft]{amsart}

\usepackage{uniform-kan-prelude}

\begin{document}

We work in the setting of a locally presentable locally cartesian closed category $\catE$.
Let $v \co \cal{J} \to \catE^\to$ be a category of finitely presentable maps, \ie having the property that source and target of $v(X)$ are finitely presentable for any $X \in \cal{J}$.

\begin{lemma}
The functor $\liftr{u}$ creates filtered colimits.
\end{lemma}

\begin{proof}
Consider a filtered diagram $F \co \cat{D} \to \liftr{J}$.
Let $(f, \phi)$ be a colimiting cone of $\liftr{v} \cc F$ in $\catE^\to$.
Our goal will be to show that $(f, \phi)$ lifts uniquely to a colimiting cone of $F$ in $\liftr{J}$.

Let us construct a $J$-right lifting structure for $f$.
Suppose we are given $X \in \cal{J}$ and a square $J X \to f$.
Since $J X$ is finitely presentable, there is $A \in \cat{D}$ such that $J X \to f$ factors through the leg $\phi_A : \liftr{v}(F A) \to f$.
Finding a filler for the square $J X \to f$ thus reduces to finding a filler for the square $J X \to \liftr{v}(F A)$; in fact, we are forced to proceed this way since we want $\phi_A$ to lift to a map of $\cal{J}$-right maps.
Since $F A$ is a $\cal{J}$-right map, we have such a filler.
The resulting filler for the square $J X \to f$ is independent of the choice of $A$ by coherence of $J$-right maps in the diagram $F$.
It is easily verified that the construction is natural in $X \in \cal{J}$.
\end{proof}

Let $(\liftr{v})_1 \co (\liftr{\cal{J}})_1 \to \catE$ denote the base change of $\liftr{v}$ along the right adjoint to $\dom_\catE$, \ie the functor $\catE \to \catE^\to$ mapping $X$ to $!_X \co X \to 1$.
Explicitly, an object of $(\liftr{\cal{J}})_1$ is $X \in \liftr{\cal{J}}$ such that $\liftr{v}(X)$ has terminal codomain.

\begin{corollary}
The functor $\liftr{u}$ creates free monads on accessible well-pointed endofunctors.
\end{corollary}

\begin{proof}
The construction of the free monad on an accessible well-pointed endofunctor proceeds by a transfinite construction via filtered colimits, thus the previous lemma applies.
\end{proof}

\begin{corollary}
The functor $\liftr{u}$ creates free monads on accessible endofunctors.
\end{corollary}

\begin{proof}
The construction of the free monad on an accessible endofunctor proceeds by a transfinite construction via filtered colimits, thus the previous lemma applies.
\end{proof}

\begin{corollary}
The functor $\liftr{u}$ creates initial algberas on accessible endofunctors.
In detail, let $F : \calE \to \calE$ be an accessible endofunctor that lifts as follows:
\[
\xymatrix{
  (\liftr{\cal{J}})_1
  \ar@{.>}[r]^{F'}
  \ar[d]
&
  (\liftr{\cal{J}})_1
  \ar[d]
\\
  \calE
  \ar[r]_{F}
&
  \calE
\rlap{.}}
\]
Then both $F$ and $F'$ admit initial algebras and we have $(\liftr{u})_1(\mu F') = \mu F$.
\end{corollary}

Assume now that pushforward along any right $\cal{J}$-map lifts to a functor between slices of $\liftr{\cal{J}}$.

\begin{corollary}
Consider morphisms $f : B \to A$, $s : B \to I$ and $t : A \to I$ where $f$ and $t$ are right $\cal{J}$-maps.
Let $F : \catE/I \to \catE/I$ denote the corresponding polynomial functor, \ie $F = \Sigma_t \Pi_f s^*$.
Then the initial algebra $\mu F \to I$ carries the structure of a right $\cal{J}$-map that furthermore makes it into an initial algebra for the lift of $F$ to $(\liftr{\cal{J}}_{/I})_1$.
\end{corollary}

\begin{proof}
Apply the previous corollary with $\calE$ replaced by $\calE/I$, noting that $s^*$, $\Pi_f$, $\Sigma_t$ all lift to functors between base changes of $(\liftr{\cal{J}}_{/I})$.
\end{proof}

\end{document}
